Experiences with Planning for Natural Language Generation

### 2009-06-04 trunk/Papers/ci-spark/experiments.tex
spell check

Fig.~\ref{fig:xtag-graph} reports the runtimes we measured in this
experiment for FF, Metric FF, and the SPUD reimplementation. We do not
report runtimes for SGPLAN, because we could not recompile SGPLAN as a
64-bit binary, and the 32-bit version ran out of memory very
quickly. We also do not report runtimes for our Java implementation of
Graphplan, because it was unusuably slow for serious problem
instances: For $k=1$ and $n=3$, it already took over two minutes, and
it exceeded its memory limit of 16 GB for $n>3$. This may be a
limitation of our naive implementation rather than the GraphPlan
algorithm itself.

Nonetheless, there are a number of observations we can make in this
experiment. First of all, the experiment confirms that FF's Enforced
Hill-Climbing search strategy works very well for the sentence
generation task: Although we are now generating with a large grammar,
FF generates a 39-word sentence ($k=1,n=6$) in under a second of
search time. This level of efficiency is a direct result of using this
particular search strategy: For $k=1$ and $n>6$, FF 2.3 (but not
Metric-FF) fell back to the best-first search strategy, which causes a
dramatic loss of search effiency. It is also encouraging that
Metric-FF still performs comparably to SPUD in terms of pure search
time. We believe that by FF's technique of evaluating actions by
estimating the distance to a goal state for the relaxed problem
essentially picks out the same evaluation function as SPUD's domain-specific
heuristic, and the enforced hill-climbing strategy needs to backtrack
very little in this domain and thus performs similarly to SPUD's
greedy search. However, SPUD's incompleteness manifests itself in this
experiment by its inability to find any plan for $k>1$ and $n>1$,
whereas FF and its variants still (correctly) find these plans.

@@

We now turn our attention to a set of experiments arising from the GIVE domain.
Besides using many of the planners from the previous set of experiments (FF,
Metric-FF, and SGPLAN), we also expand our testing to include the FF(h$_a$)
\citep{keyder08:_ff_h_plann_for_plann}, LAMA \citep{richter08:_lama_plann}, and
C$^3$ \citep{lipovetzky08:_c3} planners. Each of these additional planners
competed in the deterministic ``sequential, satifying'' track of the 2008
International Planning Competition; all planners performed well on the
competition domains, with LAMA the overall winner of the track.\footnote{See
\texttt{http://ipc.informatik.uni-freiburg.de/} for details of the 2008 IPC.}

>>>>

Fig.~\ref{fig:xtag-graph} reports the runtimes we measured in this
experiment for FF, Metric FF, and the SPUD reimplementation. We do not
report runtimes for SGPLAN, because we could not recompile SGPLAN as a
64-bit binary, and the 32-bit version ran out of memory very
quickly. We also do not report runtimes for our Java implementation of
GraphPlan, because it was unusably slow for serious problem
instances: For $k=1$ and $n=3$, it already took over two minutes, and
it exceeded its memory limit of 16 GB for $n>3$. This may be a
limitation of our naive implementation rather than the GraphPlan
algorithm itself.

Nonetheless, there are a number of observations we can make in this
experiment. First of all, the experiment confirms that FF's Enforced
Hill-Climbing search strategy works very well for the sentence
generation task: Although we are now generating with a large grammar,
FF generates a 39-word sentence ($k=1,n=6$) in under a second of
search time. This level of efficiency is a direct result of using this
particular search strategy: For $k=1$ and $n>6$, FF 2.3 (but not
Metric-FF) fell back to the best-first search strategy, which causes a
dramatic loss of search efficiency. It is also encouraging that
Metric-FF still performs comparably to SPUD in terms of pure search
time. We believe that by FF's technique of evaluating actions by
estimating the distance to a goal state for the relaxed problem
essentially picks out the same evaluation function as SPUD's domain-specific
heuristic, and the enforced hill-climbing strategy needs to backtrack
very little in this domain and thus performs similarly to SPUD's
greedy search. However, SPUD's incompleteness manifests itself in this
experiment by its inability to find any plan for $k>1$ and $n>1$,
whereas FF and its variants still (correctly) find these plans.

@@

We now turn our attention to a set of experiments arising from the GIVE domain.
Besides using many of the planners from the previous set of experiments (FF,
Metric-FF, and SGPLAN), we also expand our testing to include the FF(h$_a$)
\citep{keyder08:_ff_h_plann_for_plann}, LAMA \citep{richter08:_lama_plann}, and
C$^3$ \citep{lipovetzky08:_c3} planners. Each of these additional planners
competed in the deterministic ``sequential, satisfying'' track of the 2008
International Planning Competition; all planners performed well on the
competition domains, with LAMA the overall winner of the track.\footnote{See
\texttt{http://ipc.informatik.uni-freiburg.de/} for details of the 2008 IPC.}
